Revisiting the Truisms of Software Engineering:\\ Does Phase Delay Dramatically Increases Repair Time?

### 2015-03-02 phaseDelay.tex
working some extremes
Added Related Work section.

%\renewcommand{\baselinestretch}{0.8}
\scriptsize
\begin{center}
\begin{tabular}{r|rrr|ll}
  Sample&\multicolumn{3}{c|}{Percentiles}\\ 
size & 25th & 50th & 75th & Phase injected & Phase removed\\\hline
57& 6& 16& 47&  BeforeDevelopment&Code\\
72& 2& 4& 11&  BeforeDevelopment&CodeInspect\\
165& 6& 18& 56&  BeforeDevelopment&Test\\
50& 6& 20& 37&  BeforeDevelopment&IntTest\\
42& 8& 28& 65&  BeforeDevelopment&SysTest\\\hline

@@

\begin{figure*}[!t]

\renewcommand{\baselinestretch}{0.7} 
\begin{center}
\begin{tabular}{ll|r|rl}
            &                  & Sample\\
Phase injected & Phase removed & size & \multicolumn{2}{l}{Scale up, w.r.t. to first phase}
\input{deltas}
\end{tabular}
\end{center}
\caption{50th percentile (median) scale ups  for  time to resolve issues (taken from \fig{raw}).}
\label{fig:scale}
\end{figure*}

@@

\begin{figure*}[!t]

\renewcommand{\baselinestretch}{0.7} 
\begin{center}
\begin{tabular}{ll|r|rl}
            &                  & Sample\\
Phase injected & Phase removed & size & \multicolumn{2}{l}{Scale up, w.r.t. to first phase}
\input{deltaBig}
\end{tabular}
\end{center}
\caption{90th percentile scale ups  for  time to resolve issues .}
\label{fig:scale90}
\end{figure*}

@@

>>>>

\renewcommand{\baselinestretch}{0.7}
\scriptsize
\begin{center}
\begin{tabular}{r|rrr|ll}
  Sample&\multicolumn{3}{c|}{Percentiles}\\ 
size & 25th & 50th & 75th & Phase injected & Phase removed\\\hline
57& 6& 16& 47&  BeforeDevelopment&Code\\
72& 2& 4& 11&  BeforeDevelopment&CodeInspect\\
165& 6& 18& 56&  BeforeDevelopment&Test\\
50& 6& 20& 37&  BeforeDevelopment&IntTest\\
42& 8& 28& 65&  BeforeDevelopment&SysTest\\\hline

@@

\begin{figure}[!t]
\renewcommand{\baselinestretch}{0.7}
\scriptsize
\begin{center}
\begin{tabular}{l@{~~}|l@{~}|r@{~}|r@{~}r@{~}|r@{~}l}
           \multicolumn{2}{c}{~}                 &  &\multicolumn{2}{c|}{median}\\
  Injection&   Removal& $n$ & initial & now & \multicolumn{2}{l}{Scale up, w.r.t. initial}
\input{deltas}
\end{tabular}
\end{center}
\caption{50th percentile (median) scale ups  for  time to resolve issues (taken from \fig{raw}).}
\label{fig:scale}
\end{figure}

@@

\begin{figure}[!t]
\renewcommand{\baselinestretch}{0.7}
\scriptsize
\begin{center}
\begin{tabular}{l@{~~}|l@{~}|r@{~}|r@{~}r@{~}|r@{~}l}
           \multicolumn{2}{c}{~}                 &  &\multicolumn{2}{c|}{90th }\\
           \multicolumn{2}{c}{~}                 &  &\multicolumn{2}{c|}{percentile }\\
  Injection&   Removal& $n$ & initial & now & \multicolumn{2}{l}{Scale up, w.r.t. initial}
\input{deltaBig}
\end{tabular}
\end{center}
\caption{90th percentile scale ups.}
\label{fig:scale90}
\end{figure}

\begin{figure}[!t]
\renewcommand{\baselinestretch}{0.7}
\scriptsize
\begin{center}
\begin{tabular}{l@{~~}|l@{~}|r@{~}|r@{~}r@{~}|r@{~}l}
          \multicolumn{2}{c}{~}                 &  &\multicolumn{2}{c|}{99th }\\
           \multicolumn{2}{c}{~}                 &  &\multicolumn{2}{c|}{percentile }\\
  Injection&   Removal& $n$ & initial & now & \multicolumn{2}{l}{Scale up, w.r.t. initial}
\input{deltasBigBig}
\end{tabular}
\end{center}
\caption{99th percentile scale ups.}
\label{fig:scale90}
\end{figure}

\begin{figure}[!t]
\renewcommand{\baselinestretch}{0.7}
\scriptsize
\begin{center}
\begin{tabular}{l@{~~}|l@{~}|r@{~}|r@{~}r@{~}|r@{~}l}
           \multicolumn{2}{c}{~}                 &  &\multicolumn{2}{c|}{mean}\\
  Injection&   Removal& $n$ & initial & now & \multicolumn{2}{l}{Scale up, w.r.t. initial}
\input{deltasMean}
\end{tabular}
\end{center}
\caption{Mean  scale ups.}
\label{fig:scale90}
\end{figure}

@@

XXX post release. really hard to change? auto-updates, package managers, web-based apps.
